A Survey of Exoskeleton Control Architectures and Algorithms\\ (Draft 3.0)

### 2015-09-29 exos/exosText_MIT.tex
revision of abstract, summary, and refs

% \begin{document}
\section{MIT Exoskeleton}

@@

The specific choice of actuation for the MIT exoskeleton hip joint was a {\bf linear series elastic actuator}.  This choice provided a lightweight and relatively inexpensive means of implementing force control with a bandwidth similar to that of natural muscle.  A model of the actuator is shown in Figure \ref{fig:mitSEA}.
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/mitSEA}
  \caption{}
  \vspace{-0.2in}
 \label{fig:mitSEA}   
 \end{figure} 
Like all series elastic designs, the actuator shown in Figure \ref{fig:mitSEA} includes a spring in series with the output of the motor drive system of the actuator.  The motor-drive mechanism consists of a {\bf brushed DC motor driving a 3mm ball screw via a 2:1 reduction belt drive}.  The nut of the ball screw is coupled to the actuator output shaft via four compression die springs.  The compression of the die springs are measured using a linear potentiometer, which is how forces at the output are measured.
The team selected a {\bf 150W Maxon RE40 Brushed DC motor} for the actuator  based on the bio-mechanical data and its power and weight ratio. The force bandwidth for this actuator was characterized during both stance and swing phases of the walking gait cycle.  {\bf During stance, the bandwidth of the actuator was 35 Hz, while the bandwidth during swing was found to be 40Hz.}

@@

 The MIT exoskeleton design has a total of fourteen degrees of freedom, three at each hip, one at each knee, two at each ankle, and one in each foot.  A cam mechanism implemented at the hip joint enables hip ab/adduction.  This system was necessary because, during abduction, there is a length difference between the operator and exoskeleton leg which results from having non-collocated centers of rotation.  The cam mechanism automatically adjusts the exoskeleton leg length such that the center of rotation of the exoskeleton hip is projected onto the biological hip center of rotation.  A picture of the MIT exoskeleton is shown in Figure \ref{fig:MITsuit}.
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/MITsuit}
  \caption{}
%  \vspace{-0.2in}
 \label{fig:MITsuit}   
 \end{figure} 
% 
 The interface between the suit and operator consists of shoulder straps, a compliant waist belt, thigh cuffs, and a shoe connection.

@@

\begin{figure}[thpb]
\centering
\includegraphics[width=4.in]{exos/figs/MIT/walkingCycle}
  \caption{}
  \vspace{-0.2in}
 \label{fig:walkingCycle} 
 \end{figure} 
The walking cycle around which the MIT control scheme was designed is shown in Figure \ref{fig:walkingCycle}.  The individual control strategies in the various phases of the walking cycle are highlighted in Figure \ref{fig:walkingCycle}.  For the hip there are four distinct strategies.  During the thrust phase, the hip exerts a torque that helps to raise the center of mass of the system.  During the extension spring phase, a virtual spring stiffness allows energy to be virtually stored while the center of mass moves forward.  During the swing assist phase the virtual energy is released, resulting in a torque being applied which assists in swinging the leg forward.  Finally, in leg retraction a torque is applied to help with foot placement and weight acceptance.  A diagram that illustrates how the sensors in the shank and hip joint are used to switch between these various phases is show in Figure \ref{fig:hipControl}.
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/hipControl}
  \caption{}
  \vspace{-0.2in}
 \label{fig:hipControl} 
 \end{figure}

 The knee controller in the MIT exoskeleton effectively functions independently from he hip controller.  During knee strike, the variable damper in the knee exerts a torque proportional to the rotational velocity of the knee joint.  A residual magnetic field remains in the knee joint after it is turned off, creating a resistive torque.  The knee therefore needs to be actively demagnetized at full extension during the last phase of stance to allow it to swing freely during the subsequent swing phase.  The state machine diagram that illustrates how the various phase transitions for the knee joint were implemented using the exoskeleton's on-board sensors is in Figure \ref{fig:kneeControl}.
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/kneeControl}
  \caption{}
  \vspace{-0.2in}
 \label{fig:kneeControl} 
 \end{figure}

@@

>>>>

% \begin{document}
\section{MIT Exoskeleton}
\label{mit}
\begin{refsection}[exos/mit.bib]

@@

The specific choice of actuation for the MIT exoskeleton hip joint was a {\bf linear series elastic actuator}.  This choice provided a lightweight and relatively inexpensive means of implementing force control with a bandwidth similar to that of natural muscle.  A model of the actuator is shown in Figure \ref{fig:mitSEA}.
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/mitSEA}
  \caption{Linear series elastic actuator.}
%  \vspace{-0.2in}
 \label{fig:mitSEA}   
 \end{figure} 
Like all series elastic designs, the actuator shown in Figure \ref{fig:mitSEA} includes a spring in series with the output of the motor drive system of the actuator.  The motor-drive mechanism consists of a {\bf brushed DC motor driving a 3mm ball screw via a 2:1 reduction belt drive}.  The nut of the ball screw is coupled to the actuator output shaft via four compression die springs.  The compression of the die springs are measured using a linear potentiometer, which is how forces at the output are measured.
The team selected a {\bf 150W Maxon RE40 Brushed DC motor} for the actuator  based on the bio-mechanical data and its power and weight ratio. The force bandwidth for this actuator was characterized during both stance and swing phases of the walking gait cycle.  {\bf During stance, the bandwidth of the actuator was 35 Hz, while the bandwidth during swing was found to be 40Hz.}

@@

 The MIT exoskeleton design has a total of fourteen degrees of freedom, three at each hip, one at each knee, two at each ankle, and one in each foot.  A cam mechanism implemented at the hip joint enables hip ab/adduction.  This system was necessary because, during abduction, there is a length difference between the operator and exoskeleton leg which results from having non-collocated centers of rotation.  The cam mechanism automatically adjusts the exoskeleton leg length such that the center of rotation of the exoskeleton hip is projected onto the biological hip center of rotation.  A picture of the MIT exoskeleton is shown in Figure \ref{fig:MITsuit}.
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/MITsuit}
  \caption{ Sensors placed on the exoskeleton leg \cite{mit_control_2006}.}
%  \vspace{-0.2in}
 \label{fig:MITsuit}   
 \end{figure} 
% 
 The interface between the suit and operator consists of shoulder straps, a compliant waist belt, thigh cuffs, and a shoe connection.  The MIT exoskeleton employs a custom-built sensor that measures the interaction force between the exoskeleton and the operator?s thigh. The sensor consisted of a spring pack, where the deflection of the passive springs was measured with a spring-loaded linear potentiometer.

@@

\begin{figure}[thpb]
\centering
\includegraphics[width=4.in]{exos/figs/MIT/walkingCycle}
  \caption{ Summary of the actuation control of the exoskeleton leg as a function of gait cycle with an actuator at the hip and a damper at the knee. The ankle is completely passive but is included for completeness.}
%  \vspace{-0.2in}
 \label{fig:walkingCycle} 
 \end{figure} 
The walking cycle around which the MIT control scheme was designed is shown in Figure \ref{fig:walkingCycle}.  The individual control strategies in the various phases of the walking cycle are highlighted in Figure \ref{fig:walkingCycle}.  For the hip there are four distinct strategies.  During the thrust phase, the hip exerts a torque that helps to raise the center of mass of the system.  During the extension spring phase, a virtual spring stiffness allows energy to be virtually stored while the center of mass moves forward.  During the swing assist phase the virtual energy is released, resulting in a torque being applied which assists in swinging the leg forward.  Finally, in leg retraction a torque is applied to help with foot placement and weight acceptance.  A diagram that illustrates how the sensors in the shank and hip joint are used to switch between these various phases is show in Figure \ref{fig:hipControl}.
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/hipControl}
  \caption{State-machine diagram for the hip controller.}
%  \vspace{-0.2in}
 \label{fig:hipControl} 
 \end{figure}

 The knee controller in the MIT exoskeleton effectively functions independently from he hip controller.  During knee strike, the variable damper in the knee exerts a torque proportional to the rotational velocity of the knee joint.  A residual magnetic field remains in the knee joint after it is turned off, creating a resistive torque.  The knee therefore needs to be actively demagnetized at full extension during the last phase of stance to allow it to swing freely during the subsequent swing phase.  The state machine diagram that illustrates how the various phase transitions for the knee joint were implemented using the exoskeleton's on-board sensors is in Figure \ref{fig:kneeControl}.
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/MIT/kneeControl}
  \caption{State-machine diagram for the knee controller.}
%  \vspace{-0.2in}
 \label{fig:kneeControl} 
 \end{figure}

@@

 The hardware specifications and associated figures in this section were taken from \cite{mit_design_2006}.  The discussion on control design and and the associated figures therein are respectively based on and taken from \cite{mit_control_2006}.

 \printbibliography[heading=subbibliography]

\end{refsection}

### 2015-09-29 exos/exosText_bodyExt.tex
more edits
revision of abstract, summary, and refs

%\begin{document}
\section{Body Extender}

@@

A picture of the Body Extender exoskeleton and its five main components, four limbs and a torso, is shown in Figure \ref{fig:bodyExt}.
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/bodyExt/bodyExt}
  \caption{}
  \vspace{-0.2in}
 \label{fig:bodyExt}   
 \end{figure}

@@

 Joints that have a small range of motion and low torque requirements use linear actuators in straightforward lever mechanism configurations.  For degrees of freedom which require relatively large ranges of motion as well as torque, a motion conversion system transforms the linear actuator motion into rotational motion.  The motion conversion unit consists of a pantograph, two metallic tendons, and an output pulley connected to the output link.  A CAD drawing of the motion conversion unit is shown in Figure \ref{fig:motionConv}. 
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/bodyExt/motionConv}
  \caption{}
%  \vspace{-0.2in}
 \label{fig:motionConv}   
 \end{figure}
 There are two configurations of the motion conversion unit.  The first has a {\bf maximum continuous output of 500 Nm and the second a maximum continuous output of 270 Nm}.  The two units weigh 6 kg and 5 kg respectively, and have {\bf mechanical efficiency of about 85\%}.  {\bf The speed of the actuators is approximately 60 deg/s}.

@@

The authors in \cite{} use a decoupling strategy in their controllers which enables the individual limbs in the Body Extender to be somewhat decoupled from each other.  They claim that they accomplish this using the following model:
\begin{equation}
\mB_i(q) \ddot{q} + \mC_i(q,\dot{q})\dot{q} + \mG_{iT}(q) = {\bf \tau} + \mJ^T_{iu}F_s + \mJ^T_{ia}F_a - \mB_{iT}{q}\dot{V}_T - \mC_{iT}(q,\dot{q}){\bf V_T},
\end{equation}
where, ${\bf V_T}$ is the trunk velocity, $\mG_{iT}$ the gravitational effect of the trunk on the limb, $\mB_{iT}$ the inertia of the trunk acting on the limb, and $\mC_{iT}$ the trunk Coriolis and centrifugal term.  Note that ${\bf V_T}$ and $\dot{{\bf V}}_{\bf T}$ are directly measured through the accelerometer and gyroscope in the trunk.

@@

The dynamics of the arm when not manipulating a load are
\begin{equation}
\mB(\vq) \ddot{\vq} + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq) = {\bf \tau}. \notag
\end{equation} 
The feedback linearizing controller for this case has the form
\begin{equation}
{\bf \tau} = \mB(\vq)(\ddot{\vq}_d + K_v \dot{\tilde{\vq}} + K_p \tilde{\vq}) + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq), \notag
\end{equation}
where $\tilde{\vq} = \vq_d - \vq$.  The details are unclear in \cite{}, but it appears that the authors either propose using predefined trajectories to define $\ddot{\vq}_d$, $\dot{\vq}_d$, and $\vq_d$, or use the assumption in \eqref{eq:forceEq} to determine these values.  
%\begin{equation}
%\vF_s = \mM_p \dot{V}_e
%\label{eq:assump1}
%\end{equation}
Equation \ref{eq:forceEq} relates the measured force to the derivative of the end effector velocity $\dot{\vV}_e$.  This end effector velocity can then be related to the desired joint velocities using the analytical Jacobian transformation \[ \ddot{\vq}_d = \mJ(\vq)^{-1}(\dot{V}_e - \dot{J}(\vq,\dot{\vq})\dot{\vq}).\]  The values for $\dot{\vq}_d$ and $\vq_d$ can then be found through integration.  It is not clear the how authors explicitly decouple the human dynamics from the robot in this case.

In the case where the exoskeleton arm is manipulating a load, the feedback linearizing controller has the augmented form
\begin{equation}
{\bf \tau} = \mB(\vq)(\ddot{\vq}_d + K_v \dot{\tilde{\vq}} + K_p \tilde{\vq}) + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq) -\mJ^T(\vq) \vF_s -\mJ^T(\vq)\vF_a. \notag
\end{equation}
The main difference in this case is that the controller here explicitly compensates for the measured human-robot interaction force $\vF_s$, and the controller includes the un-sensed forces $\vF_a$ which arise from the object being manipulated.  The object interaction forces thus need to be estimated.  The ability to estimate these forces is the first fundamental assumption on which the Body Extender's control scheme relies.  Because the point at which the manipulator arm and object are connected is assumed to be well known, and the arm is instrumented with inertial sensors, estimating the interaction forces of the manipulated object is be assumed to be equivalent to estimating its inertial properties.  As outlined in \cite{}, this is accomplished using a standard regressor which uses the input and output of the feedback linearizing controller as the basis for the regression.  The details of this process are left to \cite{}.

\subsection{Opinion}

@@

In terms of the controllers highlighted in \cite{}, there are some good ideas.  For example, using a regressor to estimate unknown external forces may be an idea which is directly applicable to the TALOS project.  In the case of the Body Extender this regression is dependent on knowing at the location of the external force  relative to the suit, but the idea in general is interesting.  The idea of using the measured forces to generate desired trajectories around which a stabilizing controller is designed also appears to be a relatively good idea.  Note that, like any of the model-based control approaches outlined in the exoskeleton literature, or robotics literature for that matter, the feedback linearizing controller in this work is dependent on knowing the model of the robot hardware.

@@

@@

% S. Marcheschi, F. Salsedo, M. Fontana, and M. Bergamasco, ?Body ex- tender: Whole body exoskeleton for human power augmentation,? in Proc. IEEE Int. Conf. Robotics Automation, 2011, pp. 611?616.

>>>>

%\begin{document}
\section{Body Extender}
\label{bodyExtender}
\begin{refsection}[exos/bodyExt.bib]

@@

A picture of the Body Extender exoskeleton and its five main components, four limbs and a torso, is shown in Figure \ref{fig:bodyExt}.
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/bodyExt/bodyExt}
  \caption{The Body Extender.}
%  \vspace{-0.2in}
 \label{fig:bodyExt}   
 \end{figure}

@@

 Joints that have a small range of motion and low torque requirements use linear actuators in straightforward lever mechanism configurations.  For degrees of freedom which require relatively large ranges of motion as well as torque, a motion conversion system transforms the linear actuator motion into rotational motion.  The motion conversion unit consists of a pantograph, two metallic tendons, and an output pulley connected to the output link.  A CAD drawing of the motion conversion unit is shown in Figure \ref{fig:motionConv}. 
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/bodyExt/motionConv}
  \caption{CAD view of the internal components of the actuation module.}
%  \vspace{-0.2in}
 \label{fig:motionConv}   
 \end{figure}
 There are two configurations of the motion conversion unit.  The first has a {\bf maximum continuous output of 500 Nm and the second a maximum continuous output of 270 Nm}.  The two units weigh 6 kg and 5 kg respectively, and have {\bf mechanical efficiency of about 85\%}.  {\bf The speed of the actuators is approximately 60 deg/s}.

@@

The authors in \cite{body_control_2012} use a decoupling strategy in their controllers which enables the individual limbs in the Body Extender to be somewhat decoupled from each other.  They claim that they accomplish this using the following model:
\begin{equation}
\mB_i(q) \ddot{q} + \mC_i(q,\dot{q})\dot{q} + \mG_{iT}(q) = {\bf \tau} + \mJ^T_{iu}F_s + \mJ^T_{ia}F_a - \mB_{iT}{q}\dot{V}_T - \mC_{iT}(q,\dot{q}){\bf V_T},
\end{equation}
where, ${\bf V_T}$ is the trunk velocity, $\mG_{iT}$ the gravitational effect of the trunk on the limb, $\mB_{iT}$ the inertia of the trunk acting on the limb, and $\mC_{iT}$ the trunk Coriolis and centrifugal term.  Note that ${\bf V_T}$ and $\dot{{\bf V}}_{\bf T}$ are directly measured through the accelerometer and gyroscope in the trunk.

@@

The dynamics of the arm when not manipulating a load are
\begin{equation}
\mB(\vq) \ddot{\vq} + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq) = {\bf \tau}. \notag
\end{equation} 
The feedback linearizing controller for this case has the form
\begin{equation}
{\bf \tau} = \mB(\vq)(\ddot{\vq}_d + K_v \dot{\tilde{\vq}} + K_p \tilde{\vq}) + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq), \notag
\end{equation}
where $\tilde{\vq} = \vq_d - \vq$.  The details are unclear in \cite{body_control_2012}, but it appears that the authors either propose using predefined trajectories to define $\ddot{\vq}_d$, $\dot{\vq}_d$, and $\vq_d$, or use the assumption in \eqref{eq:forceEq} to determine these values.  
%\begin{equation}
%\vF_s = \mM_p \dot{V}_e
%\label{eq:assump1}
%\end{equation}
Equation \ref{eq:forceEq} relates the measured force to the derivative of the end effector velocity $\dot{\vV}_e$.  This end effector velocity can then be related to the desired joint velocities using the analytical Jacobian transformation \[ \ddot{\vq}_d = \mJ(\vq)^{-1}(\dot{V}_e - \dot{J}(\vq,\dot{\vq})\dot{\vq}).\]  The values for $\dot{\vq}_d$ and $\vq_d$ can then be found through integration.  It is not clear the how authors explicitly decouple the human dynamics from the robot in this case.

In the case where the exoskeleton arm is manipulating a load, the feedback linearizing controller has the augmented form
\begin{equation}
{\bf \tau} = \mB(\vq)(\ddot{\vq}_d + K_v \dot{\tilde{\vq}} + K_p \tilde{\vq}) + \mC(\vq,\dot{\vq})\dot{\vq} + \mG(\vq) -\mJ^T(\vq) \vF_s -\mJ^T(\vq)\vF_a. \notag
\end{equation}
The main difference in this case is that the controller here explicitly compensates for the measured human-robot interaction force $\vF_s$, and the controller includes the un-sensed forces $\vF_a$ which arise from the object being manipulated.  The object interaction forces thus need to be estimated.  The ability to estimate these forces is the first fundamental assumption on which the Body Extender's control scheme relies.  Because the point at which the manipulator arm and object are connected is assumed to be well known, and the arm is instrumented with inertial sensors, estimating the interaction forces of the manipulated object is be assumed to be equivalent to estimating its inertial properties.  As outlined in \cite{body_control_2012}, this is accomplished using a standard regressor which uses the input and output of the feedback linearizing controller as the basis for the regression.  The details of this process are left to \cite{body_control_2012}.

\subsection{Assessment and Recommendations}

@@

In terms of the controllers highlighted in \cite{body_control_2012}, there are some good ideas.  For example, using a regressor to estimate unknown external forces may be an idea which is directly applicable to the TALOS project.  In the case of the Body Extender this regression is dependent on knowing at the location of the external force  relative to the suit, but the idea in general is interesting.  The idea of using the measured forces to generate desired trajectories around which a stabilizing controller is designed also appears to be a relatively good idea.  Note that, like any of the model-based control approaches outlined in the exoskeleton literature, or robotics literature for that matter, the feedback linearizing controller in this work is dependent on knowing the model of the robot hardware.

@@

 The mechanical specifications as well as figures related to mechanical design for the Body Extender system discussed in this section are based on and taken from \cite{body_design_2011}.  The discussion of the control system is based on work presented in \cite{body_control_2012}.

\printbibliography[heading=subbibliography]

\end{refsection}

@@

% S. Marcheschi, F. Salsedo, M. Fontana, and M. Bergamasco, Body Extender: Whole body exoskeleton for human power augmentation, in Proc. IEEE Int. Conf. Robotics Automation, 2011, pp. 611?616.

### 2015-09-29 exos/exosText_ihmc.tex
revision of abstract, summary, and refs

% \begin{document}
\section{IHMC Mobility Assist Exoskeleton (MAE)}
Although the IHMC MAE was primarily designed as a disabled assist exoskeleton, the device is also provides a ``performance enhancement" control mode, which is within the scope of this document.  The main design principle highlighted in the IHMC MAE hardware (a recurring theme throughout exoskeleton literature) is that directly measuring user intent can be difficult for a number of reasons.  The IHMC designers resolve the issue using a new control and feedback system, which for the IHMC MAE, is primarily based on a unique actuation scheme.

@@

The spring mechanism, which sits between the gearbox and joint output, is shown in Figure \ref{fig:IHMCSEA}.  The mechanism uses linear die springs and an angular encoder to measure the joint torque output.  The choice of linear die spring was based on the spring's predictable force to displacement function as well as favorable energy storage to weight characteristics.  
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/seaAssm}
  \caption{}
  \vspace{-0.2in}
 \label{fig:IHMCSEA}   
 \end{figure}

@@

 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/ihmcSys}
  \caption{}
  \vspace{-0.2in}
 \label{fig:IHMCSYS}   
 \end{figure}

@@

 Both IHMC MAE control approaches noted are relatively straight forward implementations of low-level torque control.  The first control scheme takes full advantage of the SEA actuators' ability to directly measure output torque and subsequently to perform closed-loop torque control, (see Fig~\ref{fig:IHMCTOR}). 
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/torqueCon}
  \caption{}
  \vspace{-0.2in}
 \label{fig:IHMCTOR}   
 \end{figure}
 The controller takes in a desired torque, compares the desired value to the output torque measured at each individual actuator, then uses this value as well as its derivative to compute an actuator command signal, which in this case is a current.  The largest question in this controller, as presented in literature, is how to define the desired torque term $\tau_\text{des}$.

 The second low-level control approach presented in the IHMC MAE literature is a combination of a position-based controller with an inner-loop torque controller.  This control scheme is presented in Figure \ref{fig:IHMCPOS}.
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/positionCon}
  \caption{}
  \vspace{-0.2in}
 \label{fig:IHMCPOS}   
 \end{figure}
 The controller in Figure \ref{fig:IHMCPOS} shows an outer-loop position-based PD controller that takes in desired joint trajectories and compares them to measured joint positions.  These are used to generate desired torque values which are fed into an inner closed-loop torque control loop.  This control scheme is a good low-level choice if high-impedance. accurate suit motion is desired.  Similarly to the torque-only control loop above, the main question in this control scheme is how to obtain the desired joint trajectories.

@@

>>>>

% \begin{document}
\section{IHMC Mobility Assist Exoskeleton (MAE)}
\label{ihmc}
\begin{refsection}[exos/ihmc.bib]

Although the IHMC MAE was primarily designed as a disabled assist exoskeleton, the device is also provides a ``performance enhancement" control mode, which is within the scope of this document.  The main design principle highlighted in the IHMC MAE hardware (a recurring theme throughout exoskeleton literature) is that directly measuring user intent can be difficult for a number of reasons.  The IHMC designers resolve the issue using a new control and feedback system, which for the IHMC MAE, is primarily based on a unique actuation scheme.

@@

The spring mechanism, which sits between the gearbox and joint output, is shown in Figure \ref{fig:IHMCSEA}.  The mechanism uses linear die springs and an angular encoder to measure the joint torque output.  The choice of linear die spring was based on the spring's predictable force to displacement function as well as favorable energy storage to weight characteristics.  
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/seaAssm}
  \caption{Schematic of the RSEA elastic mechanism design, shown in the zero force position. The encoder reads a scale tape on the curved cylindrical surface. Note that the actuator housing and bearing have been omitted for clarity.}
%  \vspace{-0.2in}
 \label{fig:IHMCSEA}   
 \end{figure}

@@

 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/ihmcSys}
  \caption{Side view of the IHMC Mobility Assist Exoskeleton showing the powered and passive degrees of freedom.}
%  \vspace{-0.2in}
 \label{fig:IHMCSYS}   
 \end{figure}

@@

 Both IHMC MAE control approaches noted are relatively straight forward implementations of low-level torque control.  The first control scheme takes full advantage of the SEA actuators' ability to directly measure output torque and subsequently to perform closed-loop torque control, (see Fig~\ref{fig:IHMCTOR}). 
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/torqueCon}
  \caption{Torque control loop in the actuator control system.}
%  \vspace{-0.2in}
 \label{fig:IHMCTOR}   
 \end{figure}
 The controller takes in a desired torque, compares the desired value to the output torque measured at each individual actuator, then uses this value as well as its derivative to compute an actuator command signal, which in this case is a current.  The largest question in this controller, as presented in literature, is how to define the desired torque term $\tau_\text{des}$.

 The second low-level control approach presented in the IHMC MAE literature is a combination of a position-based controller with an inner-loop torque controller.  This control scheme is presented in Figure \ref{fig:IHMCPOS}.
  \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/ihmc/positionCon}
  \caption{Control system diagram for an actuator. The torque feedback is fed to an inner control loop while the position is fed back to the overall position controller.}
%  \vspace{-0.2in}
 \label{fig:IHMCPOS}   
 \end{figure}
 The controller in Figure \ref{fig:IHMCPOS} shows an outer-loop position-based PD controller that takes in desired joint trajectories and compares them to measured joint positions.  These are used to generate desired torque values which are fed into an inner closed-loop torque control loop.  This control scheme is a good low-level choice if high-impedance. accurate suit motion is desired.  Similarly to the torque-only control loop above, the main question in this control scheme is how to obtain the desired joint trajectories.

@@

All of the figures as well as hardware and control specifications in this section are taken from \cite{ihmc_2009}.

\printbibliography[heading=subbibliography]

\end{refsection}

### 2015-09-29 exos/exosText_roboKnee.tex
revision of abstract, summary, and refs

% \begin{document}
\section{RoboKnee}

@@

The actuator used in the RoboKnee device (see Figure \ref{fig:roboAct}) consists of a drive train and output carriage. These two sub-assemblies are coupled through die compression springs.  A servo motor directly connected to a ball screw assembly drives a ball nut flange that pushes on a spring retaining plate.  A secondary spring retaining plate is coupled to an output assembly.  By measuring the deflection in the die springs, RoboKnee is able to obtain the force applied to the output of the linear SEA.  
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/roboKnee/roboSEA}
  \caption{}
  \vspace{-0.2in}
 \label{fig:roboAct}   
 \end{figure}

@@

 The RoboKnee device is composed of an off-the-shelf knee brace modified with structural pieces to extend the brace and provide actuator attachment points (see Figure~\ref{fig:roboKnee}).
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/roboKnee/roboBrace}
  \caption{}
  \vspace{-0.2in}
 \label{fig:roboKnee}   
 \end{figure}
 The exact length between actuator attachment points is not listed in the literature, but it appears as though the attachment points are at a minimum of one actuator stroke displacement away from each other. Thus, we assume a {\bf minimum moment arm of 30.5 cm} is a reasonable approximation.

@@

 The overall design of the RoboKnee mechanism is most likely not the greatest, as it significantly increases the effective volume of the operator-system leg, but as a prototype, this concept offers interesting benefits.

>>>>

% \begin{document}
\section{RoboKnee}
\label{roboKnee}
\begin{refsection}[exos/roboKnee.bib]

@@

The actuator used in the RoboKnee device (see Figure \ref{fig:roboAct}) consists of a drive train and output carriage. These two sub-assemblies are coupled through die compression springs.  A servo motor directly connected to a ball screw assembly drives a ball nut flange that pushes on a spring retaining plate.  A secondary spring retaining plate is coupled to an output assembly.  By measuring the deflection in the die springs, RoboKnee is able to obtain the force applied to the output of the linear SEA.  
\begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/roboKnee/roboSEA}
  \caption{Exploded view of a series-elastic actuator.}
%  \vspace{-0.2in}
 \label{fig:roboAct}   
 \end{figure}

@@

 The RoboKnee device is composed of an off-the-shelf knee brace modified with structural pieces to extend the brace and provide actuator attachment points (see Figure~\ref{fig:roboKnee}).
 \begin{figure}[thpb]
\centering
\includegraphics[width=3.in]{exos/figs/roboKnee/roboBrace}
  \caption{RoboKnee design.}
%  \vspace{-0.2in}
 \label{fig:roboKnee}   
 \end{figure}
 The exact length between actuator attachment points is not listed in the literature, but it appears as though the attachment points are at a minimum of one actuator stroke displacement away from each other. Thus, we assume a {\bf minimum moment arm of 30.5 cm} is a reasonable approximation.

@@

 The overall design of the RoboKnee mechanism is most likely not optimal, as it significantly increases the effective volume of the operator-system leg, but as a prototype, this concept offers interesting benefits.

 The discussion as well as figures in this section are respectively based on and taken from \cite{robo_knee_2004}.

\printbibliography[heading=subbibliography]

\end{refsection}
